Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-09 paper.tex
fixing SI and trying to understand plot
weird behavior in the plot after changing FC and HT integrals.

@@

This paper investigates the microscopic parameters that control HDFG output. \cite{Bonn2024, McDonnell2024}
In \autoref{steadystate}, we first identify the vibrational selection rules. 
The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments. \cite{Kaufman2024}

Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}
	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
Under the electric dipole approximation, $V(t) = -\vec{\mu} \cdot \sum_{j} E_j(t)$, where $j$ indexes the input electric fields.
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ is a complex function which can be modified to include system-bath interactions, solvent-solute coupling, etc. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}_R = \Gamma \rho$.
This limit which has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy. \cite{Gaynor2017} 
Experimentally, it has been shown to be valid when investigating doubly resonant SFG response using pulses much longer than electronic dephasing times. \cite{Raschke2002}
This limit is taken to emphasize the quantum mechanical selection rules of the HDFG technique.

@@

It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho} = 0$). \cite{Simpson2004, Moad2005}
Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
\begin{equation} \label{polarization}
{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(\omega_1) 
\end{equation}
where $\chi^{(3)}_{IJKL}$ is the $IJKL$ element of the third order electrical susceptibility, a rank four tensor, generally written as
\begin{equation}\label{eq:nfgamma}
	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle.
\end{equation}
Here $N$ is a number density and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
The brackets indicate an orientational average.\cite{Andrews1977}
Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
$F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index. \cite{Bedeaux1973}

By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
\begin{equation}\label{sivegamma}
		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho_{gg}
\end{equation}
where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for simplicity.
$D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
For a HDFG experiment using two (three) distinct, non-degenerate input fields, $D = 3 (6)$.

@@

\subsection{Vibronic Selection Rules}\label{Albrecht}
While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter. \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.

For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,\tilde{v}'} \frac{
		R_{i}^{gv, e\tilde{v}'} 
		R_{j}^{e\tilde{v}',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{	\Delta_{e\tilde{v}', gv}
		\Delta_{mn, gv}
		\Delta_{g0,gv}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
It is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
\begin{equation}\label{gammaabc}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions. 
The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where $H$ is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
		It is assumed that $\omega_2 = \omega_3$.
		Note that (b) plots magnitudes of the labeled quantities.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
	\label{fig:doubres_spec}
\end{figure*}

@@

In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e\tilde{v}',gv}^{-1}$.
We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
The belief arises from the approximation $\abs{\omega_{e\tilde{v}',gv} - 2\omega_2} \gg 2\Gamma_{e\tilde{v}',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
This means that it is difficult to isolate $B$ terms when $A$ terms are present.
As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
	\begin{ruledtabular}
		\begin{tabular}{cccc}
			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
			\hline  
			$A$ 
			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = 0.27 $ 
			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\

			$B_1$ 
			& $\langle 1 | \tilde{0} \rangle \mel{\tilde{0}}{Q}{0} = -0.08$ 
			& $\langle 1 | \tilde{1} \rangle \mel{\tilde{1}}{Q}{0} = 0.48$ 
			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = 0.14$\\

			$B_2$ 
			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.55$  
			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = -0.07$ 
			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.08$\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

>>>>

Nonlinear spectroscopic probes of electronic-vibrational coupling are not limited to the Raman and hyper-Raman based techniques diagrammed in \autoref{fig:comparisonwmel}.
Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
\textbf{add some more words, compare and contrast just a hair}

@@

This paper investigates the microscopic parameters that control HDFG output. \cite{RN352, Bonn2024, McDonnell2024}
HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments. \cite{Kaufman2024}  
In \autoref{steadystate}, we first identify the vibrational selection rules. 
The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
Under the electric dipole approximation, $V(t) = -\vec{\mu} \cdot \sum_{j} E_j(t)$, where $j$ indexes the input electric fields.
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ is a complex function which can be modified to include system-bath interactions, solvent-solute coupling, etc. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation, where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}_R = \Gamma \rho$.
This limit which has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy. \cite{Gaynor2017} 
Experimentally, it has been shown to be valid when investigating doubly resonant SFG response using pulses much longer than electronic dephasing times. \cite{Raschke2002}
This limit is taken to emphasize the quantum mechanical selection rules of the HDFG technique.

@@

It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho} = 0$). \cite{Simpson2004, Moad2005}
Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
\begin{equation} \label{polarization}
{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(\omega_1) 
\end{equation}
where $\chi^{(3)}_{IJKL}$ is the $IJKL$ element of the third order electrical susceptibility, a rank four tensor, generally written as
\begin{equation}\label{eq:nfgamma}
	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle_{IJKL}.
\end{equation}
Here $N$ is a number density and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
The brackets indicate an orientational average.\cite{Andrews1977}
Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
$F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index. \cite{Bedeaux1973}

By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{RN442, RN133}
\begin{equation}\label{sivegamma}
		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho_{gg}
\end{equation}
where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for simplicity.
$D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
For a HDFG experiment using two (three) distinct, non-degenerate input fields, $D = 3 (6)$.

@@

\subsection{Vibronic Selection Rules}\label{Albrecht}
While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter. \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.

For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,\tilde{v}'} \frac{
		R_{i}^{gv, e\tilde{v}'} 
		R_{j}^{e\tilde{v}',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{	\Delta_{e\tilde{v}', gv}
		\Delta_{mn, gv}
		\Delta_{g0,gv}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
It is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
\begin{equation}\label{gammaabc}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions. 
The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into HDFG selection rules.

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
		It is assumed that $\omega_2 = \omega_3$.
		Note that (b) plots magnitudes of the labeled quantities.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 800 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
	\label{fig:doubres_spec}
\end{figure*}

@@

In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e\tilde{v}',gv}^{-1}$.
We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
The belief arises from the approximation that when $\abs{\omega_{e\tilde{v}',gv} - 2\omega_2} \gg 2\Gamma_{e\tilde{v}',gv}$, $A$ vanishes through a closure relationship.\cite{Neddersen1989}
As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
This means that it is difficult to isolate $B$ terms when $A$ terms are present.
As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
	\begin{ruledtabular}
		\begin{tabular}{cccc}
			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
			\hline  
			$A$ 
			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = -0.31 $  
			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = 0.27 $ 
			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = 0.04$\\

			$B_1$ 
			& $\langle 1 | \tilde{0} \rangle \mel{\tilde{0}}{Q}{0} = -0.08$ 
			& $\langle 1 | \tilde{1} \rangle \mel{\tilde{1}}{Q}{0} = 0.48$ 
			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = -0.14$\\

			$B_2$ 
			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.70$  
			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = 0.07$ 
			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.08$\\
		\end{tabular}
	\end{ruledtabular}
\end{table}
